Data Hygiene Gotchas

### 2016-08-23 articles/articles.Rmd
fix typos

>>>>

- Cameron Davidson Pilon: Mistakes I've Made. [[Youtube](https://www.youtube.com/watch?v=VWtsTIbFXxA)]
    - Always be aware of the sample sizes when computing aggregated data.
    - Correlated data can lead to misinterpretation of the results.
- Data Science: Beyond the Kaggle. [[Blog](http://datawrangl.com/2016/05/15/data-science-beyond-the-kaggle/)]
- Mentality for hackathons. [[Medium](https://medium.com/data-engineering/modeling-madly-8b2c72eb52be#.q9ly8hxq2)]
- The top 5 habits of a professional data scientist. [[OREILLY](https://www.oreilly.com/learning/theres-nothing-magical-about-learning-data-science?imm_mid=0e6c5a&cmp=em-data-na-na-newsltr_20160817)]

### 2016-08-23 articles/data_hygiene/data_hygiene.Rmd
calendar heatmap
fix typos

**Little variability** e.g. 99% of all the data points have the same category for one of the feauters. If we have a large amount of data, and there is reasonable number of data points (the notion of reasonable really depends on our judgement, at least 30 ...?), then including it in the model is a viable choice. Otherwise it makes sense to drop it (even better, understand why it occured).

@@

- New data can't be predicted due to "unseen" category.

@@

@@

Sometimes, it makes more sense to represent a numerical attribute as a categorical one. The idea is to reduce the noise endured by the learning algorithm, by assigning certain ranges of a numerical attribute to distinct ‘buckets’. Consider the problem of predicting whether a person owns a certain item of clothing or not. Age might definitely be a factor here. What is actually more pertinent, is the Age Group. So what we could do, is have ranges such as 1-10, 11-18, 19-25, 26-40, etc. Moreover, instead of decomposing these categories as in point 2, we could just use scalar values, since age groups that lie "closer by" do represent similar properties.

>>>>

**Little variability** e.g. 99% of all the data points have the same category for one of the features. If we have a large amount of data, and there is reasonable number of data points (the notion of reasonable really depends on our judgement, at least 30 ...?), then including it in the model is a viable choice. Otherwise it makes sense to drop it (even better, understand why it occured).

@@

@@

**Unseen Category** Another thing we might be to check is whether the out test data contains "unseen" category during the modeling phase.

@@

Sometimes, it makes more sense to represent a numerical attribute as a categorical one. The idea is to reduce the noise endured by the learning algorithm, by assigning certain ranges of a numerical attribute to distinct ‘buckets’. Consider the problem of predicting whether a person owns a certain item of clothing or not. Age might definitely be a factor here. What is actually more pertinent, is the Age Group. So what we could do, is have ranges such as 1-10, 11-18, 19-25, 26-40, etc. Moreover, instead of doing one hot encoding this these binned categories, we could just use scalar values, since age groups that lie "closer by" do represent similar properties.
